---
title: "Airbnb Analysis"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(stringr)
library(zipcode)
library(dplyr)
library(sqldf)
library(data.table)
library(gbm)
library(randomForest)
library(ranger)
```

Reading the file: The Airbnb dataset

```{r}
getwd()
rm(list = ls())
setwd('/Users/shashank/Desktop/Semester 1/Frameworks 1/Kaggle competition/')
data = read.csv('analysisData.csv', na.strings = c("NA","N/A"," "))
```

Analysisng the dataset
```{r}
colnames(data)
str(data)
sapply(data, class)
```


Counting na values in each column

```{r}
colSums(is.na(data))
```

Converting character to numneric datatypes for applicable columns such as number of host listings, total listings and beds

```{r}
data$host_listings_count = as.numeric(data$host_listings_count)
data$host_total_listings_count = as.numeric(data$host_total_listings_count)
data$beds = as.numeric(data$beds)
```

Converting the date to days starting from today

```{r}

data$first_review_day = as.Date(Sys.Date())-as.Date(data$first_review)
data$last_review_day = as.Date(Sys.Date())-as.Date(data$last_review)
data$host_since_day = as.Date(Sys.Date())-as.Date(data$host_since)

```

Counting characters to see correlation between review lengths and rating

```{r}

data$name_nchar<-nchar(as.character(data$name), type = 'chars')
data$description_nchar<-nchar(as.character(data$description), type = 'chars')
data$neighborhood_overview_nchar<-nchar(as.character(data$neighborhood_overview), type = 'chars')
data$summary_nchar<-nchar(as.character(data$summary), type = 'chars')
data$space_nchar<-nchar(as.character(data$space), type = 'chars')
data$notes_nchar<-nchar(as.character(data$notes), type = 'chars')
data$access_nchar<-nchar(as.character(data$access), type = 'chars')
data$interaction_nchar<-nchar(as.character(data$interaction), type = 'chars')

```

counting number of amenities

```{r}
data$amenities_nchar = str_count(data$amenities, ',')
```

Replacing the NA with mean or mode

```{r}
data$cleaning_fee[which(is.na(data$cleaning_fee))] = 0
data$security_deposit[which(is.na(data$security_deposit))] = 0
data$beds[which(is.na(data$beds))] = 0
data$host_total_listings_count[which(is.na(data$host_total_listings_count))] = mean(data$host_total_listings_count, na.rm = TRUE)
data$host_listings_count[which(is.na(data$host_listings_count))] = mean(data$host_listings_count, na.rm = TRUE) 
data$reviews_per_month[which(is.na(data$reviews_per_month))] = mean(data$reviews_per_month, na.rm = TRUE) 
data$host_since_day[is.na(data$host_since_day)] = mean(data$host_since_day[!is.na(data$host_since_day)])
data$description_nchar[is.na(data$description_nchar)] = 0
data$summary_nchar[is.na(data$summary_nchar)] = 0
data$notes_nchar[is.na(data$notes_nchar)] = 0
data$access_nchar[is.na(data$access_nchar)] = 0
data$interaction_nchar[is.na(data$interaction_nchar)] = 0

```

Removing the Outliers from various varibales by plotting them and checking for outliers

```{r}
# MAXIMUM_NIGHTS
mask_maximum_nights_outlier = (data$maximum_nights>6000)
data[mask_maximum_nights_outlier, 'maximum_nights'] = median(data$maximum_nights,na.rm = T)
summary(data$maximum_nights)
plot(data$maximum_nights)
```


```{r}
# MINIMUM_MAXIMUM_NIGHTS
mask_minimum_maximum_nights_outlier = (data$minimum_maximum_nights>6000)
data[mask_minimum_maximum_nights_outlier, 'minimum_maximum_nights'] = median(data$minimum_maximum_nights,na.rm = T)
summary(data$minimum_maximum_nights)
plot(data$minimum_maximum_nights)
```


```{r}
# MAXIMUM_MAXIMUM_NIGHTS
mask_maximum_maximum_nights_outlier = (data$maximum_maximum_nights>6000)
data[mask_maximum_maximum_nights_outlier, 'maximum_maximum_nights'] = median(data$maximum_maximum_nights,na.rm = T)
summary(data$maximum_maximum_nights)
plot(data$maximum_maximum_nights)
```


```{r}
# MAXIMUM_MAXIMUM_NIGHTS_AVG
mask_maximum_nights_avg_ntm_outlier = (data$maximum_nights_avg_ntm>6000)
data[mask_maximum_nights_avg_ntm_outlier, 'maximum_nights_avg_ntm'] = median(data$maximum_nights_avg_ntm,na.rm = T)
summary(data$maximum_nights_avg_ntm)
plot(data$maximum_nights_avg_ntm)
```

Removing rows which are not good data points!

```{r}
ggplot(data=data, aes(x=price)) + 
  geom_histogram(fill="blue", binwidth = 10)

table(data$price)       # 15 rows have Price = 0, which is not good data

# Remove Rows which have Price = 0, these are not good values

data = data[!data$price==0,]
table(data$price)
```

Adding levels to factors

```{r}
levels(data$neighbourhood_cleansed) <- c(levels(data$neighbourhood_cleansed), "Howland Hook", "New Dorp", "New Dorp Beach")
levels(data$property_type) <- c(levels(data$property_type), "Casa particular (Cuba)", "Castle", "Farm stay")
```

Read scoring data

```{r}
scoringData = read.csv('scoringData.csv', na.strings = c("NA","N/A"," "))
```

Applying all the above operations to the scoring Data

```{r}
scoringData$property_type = factor(scoringData$property_type, levels = levels(data$property_type))
scoringData$neighbourhood_cleansed = factor(scoringData$neighbourhood_cleansed, levels = levels(data$neighbourhood_cleansed))

#counting na values in each column
colSums(is.na(scoringData))

#converting cahracter to numneric
scoringData$host_listings_count = as.numeric(scoringData$host_listings_count)
scoringData$host_total_listings_count = as.numeric(scoringData$host_total_listings_count)
scoringData$beds = as.numeric(scoringData$beds)


#converting date to days from today
scoringData$first_review_day = as.Date(Sys.Date())-as.Date(scoringData$first_review)
scoringData$last_review_day = as.Date(Sys.Date())-as.Date(scoringData$last_review)
scoringData$host_since_day = as.Date(Sys.Date())-as.Date(scoringData$host_since)

#counting characters
scoringData$name_nchar = nchar(as.character(scoringData$name), type = 'chars')
scoringData$description_nchar = nchar(as.character(scoringData$description), type = 'chars')
scoringData$neighborhood_overview_nchar = nchar(as.character(scoringData$neighborhood_overview), type = 'chars')
scoringData$summary_nchar = nchar(as.character(scoringData$summary), type = 'chars')
scoringData$space_nchar = nchar(as.character(scoringData$space), type = 'chars')
scoringData$notes_nchar = nchar(as.character(scoringData$notes), type = 'chars')
scoringData$access_nchar = nchar(as.character(scoringData$access), type = 'chars')
scoringData$interaction_nchar = nchar(as.character(scoringData$interaction), type = 'chars')

#number of amenities
scoringData$amenities_nchar = str_count(scoringData$amenities, ',')


#replacing NA with mean or mode
scoringData$cleaning_fee[which(is.na(scoringData$cleaning_fee))] = 0
scoringData$security_deposit[which(is.na(scoringData$security_deposit))] = 0
scoringData$beds[which(is.na(scoringData$beds))] = 0
scoringData$host_total_listings_count[which(is.na(scoringData$host_total_listings_count))] = mean(scoringData$host_total_listings_count, na.rm = TRUE)
scoringData$host_listings_count[which(is.na(scoringData$host_listings_count))] = mean(scoringData$host_listings_count, na.rm = TRUE) 
scoringData$reviews_per_month[which(is.na(scoringData$reviews_per_month))] = mean(scoringData$reviews_per_month, na.rm = TRUE) 
scoringData$host_since_day[is.na(scoringData$host_since_day)] = mean(scoringData$host_since_day[!is.na(scoringData$host_since_day)])
scoringData$description_nchar[is.na(scoringData$description_nchar)] = 0
scoringData$summary_nchar[is.na(scoringData$summary_nchar)] = 0
scoringData$notes_nchar[is.na(scoringData$notes_nchar)] = 0
scoringData$access_nchar[is.na(scoringData$access_nchar)] = 0
scoringData$interaction_nchar[is.na(scoringData$interaction_nchar)] = 0
#scoringData$property_type[is.na(scoringData$property_type)] = "Apartment"
#scoringData$neighbourhood_cleansed[is.na(scoringData$neighbourhood_cleansed)] = "Williamsburg"

# OUTLIERS

# MAXIMUM_NIGHTS
mask_maximum_nights_outlier1 = (scoringData$maximum_nights>6000)
scoringData[mask_maximum_nights_outlier1, 'maximum_nights'] = median(scoringData$maximum_nights,na.rm = T)
summary(data$maximum_nights)

# MINIMUM_MAXIMUM_NIGHTS
mask_minimum_maximum_nights_outlier1 = (scoringData$maximum_nights>6000)
scoringData[mask_minimum_maximum_nights_outlier1, 'minimum_maximum_nights'] = median(scoringData$minimum_maximum_nights,na.rm = T)

# MAXIMUM_MAXIMUM_NIGHTS
mask_maximum_maximum_nights_outlier1 = (scoringData$maximum_maximum_nights>6000)
scoringData[mask_maximum_maximum_nights_outlier1, 'maximum_maximum_nights'] = median(scoringData$maximum_maximum_nights,na.rm = T)


# MAXIMUM_MAXIMUM_NIGHTS
mask_maximum_nights_avg_ntm_outlier1 = (scoringData$maximum_nights_avg_ntm>6000)
scoringData[mask_maximum_nights_avg_ntm_outlier1, 'maximum_nights_avg_ntm'] = median(scoringData$maximum_nights_avg_ntm,na.rm = T)
```

Using Zipcodes to extract location data accurately

```{r}
#Zipcoding
data$zipcode[data$zipcode == ""] <- "10002"
scoringData$zipcode[scoringData$zipcode == ""] <- "10002"

data$zipcode[data$zipcode == "11249\n11249"] <- "11249"
scoringData$zipcode[scoringData$zipcode == "11249\n11249"] <- "11249"

data$zipcode[data$zipcode == "11385-2308"] <- "11385"
scoringData$zipcode[scoringData$zipcode == "11385-2308"] <- "11385"

data$zipcode[data$zipcode == "11413-3220"] <- "11413"
scoringData$zipcode[scoringData$zipcode == "11413-3220"] <- "11413"

data$zipcode[data$zipcode == "11103-3233"] <- "11103"
scoringData$zipcode[scoringData$zipcode == "11103-3233"] <- "11103"

data$zipcode[data$zipcode == "111211"] <- "11221"
scoringData$zipcode[scoringData$zipcode == "111211"] <- "11221"

data$zipcode[data$zipcode == "1m"] <- "10002"
scoringData$zipcode[scoringData$zipcode == "1m"] <- "10002"


data("zipcode")
data <- merge(x = data, y = zipcode, by.x = "zipcode", by.y = "zip")
scoringData <- merge(x = scoringData, y = zipcode, by.x = "zipcode", by.y = "zip")
```

Finding keywords such as luxury, Luxury, luxurious and Luxurious which might affect pricing 

```{r}
# luxury
data$luxury1 = data$name %like% "luxury"
scoringData$luxury1 = scoringData$name %like% "luxury"
data$luxury1 = as.numeric(as.logical(data$luxury1))
scoringData$luxury1 = as.numeric(as.logical(scoringData$luxury1))

data$luxury2 = data$summary %like% "luxury"
scoringData$luxury2 = scoringData$summary %like% "luxury"
data$luxury2 = as.numeric(as.logical(data$luxury2))
scoringData$luxury2 = as.numeric(as.logical(scoringData$luxury2))

data$luxury3 = data$space %like% "luxury"
scoringData$luxury3 = scoringData$space %like% "luxury"
data$luxury3 = as.numeric(as.logical(data$luxury3))
scoringData$luxury3 = as.numeric(as.logical(scoringData$luxury3))

data$luxury4 = data$description %like% "luxury"
scoringData$luxury4 = scoringData$description %like% "luxury"
data$luxury4 = as.numeric(as.logical(data$luxury4))
scoringData$luxury4 = as.numeric(as.logical(scoringData$luxury4))

data$luxury5 = data$neighborhood_overview %like% "luxury"
scoringData$luxury5 = scoringData$neighborhood_overview %like% "luxury"
data$luxury5 = as.numeric(as.logical(data$luxury5))
scoringData$luxury5 = as.numeric(as.logical(scoringData$luxury5))

# Luxury
data$luxury6 = data$name %like% "Luxury"
scoringData$luxury6 = scoringData$name %like% "Luxury"
data$luxury6 = as.numeric(as.logical(data$luxury6))
scoringData$luxury6 = as.numeric(as.logical(scoringData$luxury6))

data$luxury7 = data$summary %like% "Luxury"
scoringData$luxury7 = scoringData$summary %like% "Luxury"
data$luxury7 = as.numeric(as.logical(data$luxury7))
scoringData$luxury7 = as.numeric(as.logical(scoringData$luxury7))

data$luxury8 = data$space %like% "Luxury"
scoringData$luxury8 = scoringData$space %like% "Luxury"
data$luxury8 = as.numeric(as.logical(data$luxury8))
scoringData$luxury8 = as.numeric(as.logical(scoringData$luxury8))

data$luxury9 = data$description %like% "Luxury"
scoringData$luxury9 = scoringData$description %like% "Luxury"
data$luxury9 = as.numeric(as.logical(data$luxury9))
scoringData$luxury9 = as.numeric(as.logical(scoringData$luxury9))

data$luxury10 = data$neighborhood_overview %like% "Luxury"
scoringData$luxury10 = scoringData$neighborhood_overview %like% "Luxury"
data$luxury10 = as.numeric(as.logical(data$luxury10))
scoringData$luxury10 = as.numeric(as.logical(scoringData$luxury10))

# luxurious
data$luxury11 = data$name %like% "luxurious"
scoringData$luxury11 = scoringData$name %like% "luxurious"
data$luxury11 = as.numeric(as.logical(data$luxury11))
scoringData$luxury11 = as.numeric(as.logical(scoringData$luxury11))

data$luxury12 = data$summary %like% "luxurious"
scoringData$luxury12 = scoringData$summary %like% "luxurious"
data$luxury12 = as.numeric(as.logical(data$luxury12))
scoringData$luxury12 = as.numeric(as.logical(scoringData$luxury12))

data$luxury13 = data$space %like% "luxurious"
scoringData$luxury13 = scoringData$space %like% "luxurious"
data$luxury13 = as.numeric(as.logical(data$luxury13))
scoringData$luxury13 = as.numeric(as.logical(scoringData$luxury13))

data$luxury14 = data$description %like% "luxurious"
scoringData$luxury14 = scoringData$description %like% "luxurious"
data$luxury14 = as.numeric(as.logical(data$luxury14))
scoringData$luxury14 = as.numeric(as.logical(scoringData$luxury14))

data$luxury15 = data$neighborhood_overview %like% "luxurious"
scoringData$luxury15 = scoringData$neighborhood_overview %like% "luxurious"
data$luxury15 = as.numeric(as.logical(data$luxury15))
scoringData$luxury15 = as.numeric(as.logical(scoringData$luxury15))

# Luxurious
data$luxury16 = data$name %like% "Luxurious"
scoringData$luxury16 = scoringData$name %like% "Luxurious"
data$luxury16 = as.numeric(as.logical(data$luxury16))
scoringData$luxury16 = as.numeric(as.logical(scoringData$luxury16))

data$luxury17 = data$summary %like% "Luxurious"
scoringData$luxury17 = scoringData$summary %like% "Luxurious"
data$luxury17 = as.numeric(as.logical(data$luxury17))
scoringData$luxury17 = as.numeric(as.logical(scoringData$luxury17))

data$luxury18 = data$space %like% "Luxurious"
scoringData$luxury18 = scoringData$space %like% "Luxurious"
data$luxury18 = as.numeric(as.logical(data$luxury18))
scoringData$luxury18 = as.numeric(as.logical(scoringData$luxury18))

data$luxury19 = data$description %like% "Luxurious"
scoringData$luxury19 = scoringData$description %like% "Luxurious"
data$luxury19 = as.numeric(as.logical(data$luxury19))
scoringData$luxury19 = as.numeric(as.logical(scoringData$luxury19))

data$luxury20 = data$neighborhood_overview %like% "Luxurious"
scoringData$luxury20 = scoringData$neighborhood_overview %like% "Luxurious"
data$luxury20 = as.numeric(as.logical(data$luxury20))
scoringData$luxury20 = as.numeric(as.logical(scoringData$luxury20))


data$luxury = (data$luxury1 + data$luxury2 + data$luxury3 + data$luxury4 + data$luxury5 + data$luxury6 + data$luxury7 + data$luxury8 + data$luxury9 + data$luxury10
               + data$luxury11 + data$luxury12 + data$luxury13 + data$luxury14 + data$luxury15 + data$luxury16 + data$luxury17 + data$luxury18 + data$luxury19 
               + data$luxury20)

scoringData$luxury = (scoringData$luxury1 + scoringData$luxury2 + scoringData$luxury3 + scoringData$luxury4 + scoringData$luxury5 + scoringData$luxury6
                      + scoringData$luxury7 + scoringData$luxury8 + scoringData$luxury9 + scoringData$luxury10 + scoringData$luxury11 + scoringData$luxury12
                      + scoringData$luxury13 + scoringData$luxury14 + scoringData$luxury15 + scoringData$luxury16 + scoringData$luxury17 + scoringData$luxury18
                      + scoringData$luxury19 + scoringData$luxury20)
```

Finding keywords such as bus,train,subway which might affect pricing since more transportation means higher price

```{r}
data$transit_bus = data$transit %like% "bus"
scoringData$transit_bus = scoringData$name %like% "bus"
data$transit_bus = as.numeric(as.logical(data$transit_bus))
scoringData$transit_bus = as.numeric(as.logical(scoringData$transit_bus))

data$transit_bus1 = data$transit %like% "buses"
scoringData$transit_bus1 = scoringData$name %like% "bus"
data$transit_bus1 = as.numeric(as.logical(data$transit_bus1))
scoringData$transit_bus1 = as.numeric(as.logical(scoringData$transit_bus1))

data$transit_train = data$transit %like% "train"
scoringData$transit_train = scoringData$name %like% "train"
data$transit_train = as.numeric(as.logical(data$transit_train))
scoringData$transit_train = as.numeric(as.logical(scoringData$transit_train))

data$transit_subway = data$transit %like% "subway"
scoringData$transit_subway = scoringData$name %like% "subway"
data$transit_subway = as.numeric(as.logical(data$transit_subway))
scoringData$transit_subway = as.numeric(as.logical(scoringData$transit_subway))

data$transit_modes = data$transit_bus + data$transit_subway + data$transit_train
scoringData$transit_modes = scoringData$transit_bus + scoringData$transit_subway + scoringData$transit_train
```

Applying linear model and for predicting prices and removing non essential variables from the model.

```{r}
model1 = lm(price~ 
              host_total_listings_count
            + host_is_superhost 
            + host_has_profile_pic
#            + host_identity_verified
            + is_location_exact
            + property_type
            + neighbourhood_group_cleansed
            + room_type
            + accommodates
            + security_deposit
            + cleaning_fee
            + guests_included
            + extra_people
            + minimum_nights
            + maximum_maximum_nights
            + minimum_maximum_nights
            + maximum_nights
            + review_scores_rating
            + bathrooms
            + bedrooms
            + beds
            + bed_type
            + availability_30
            + availability_60
            + availability_90
            + availability_365
            + neighbourhood_cleansed
            + number_of_reviews
            + number_of_reviews_ltm 
            + review_scores_accuracy 
            + review_scores_cleanliness
            + review_scores_checkin
#           + review_scores_communication 
#            + review_scores_location 
            + review_scores_value 
#            + reviews_per_month 
#            + instant_bookable 
            + cancellation_policy 
#            + require_guest_profile_picture 
#            + require_guest_phone_verification      
            + calculated_host_listings_count 
            + calculated_host_listings_count_entire_homes 
            + calculated_host_listings_count_private_rooms
            +  name_nchar
#            + description_nchar 
#            +neighborhood_overview_nchar 
            + summary_nchar 
            + space_nchar 
#           + notes_nchar 
#            + access_nchar 
#           + interaction_nchar
            + amenities_nchar 
            + first_review_day 
            + last_review_day 
            + latitude
            + longitude
            + luxury
            + transit_modes
#           + host_since_day 

,data)
summary(model1)$r.squared
summary(model1)$adj.r.squared
```

Applying random forest model and for predicting prices and removing non essential variables from the model.


```{r eval=FALSE, include=FALSE}
#Random forest model


set.seed(617)
model2 = randomForest(price~ host_total_listings_count
                      + host_is_superhost 
                      + host_has_profile_pic
                      #            + host_identity_verified
                      + is_location_exact
                      + property_type
                      + neighbourhood_group_cleansed
                      + room_type
                      + accommodates
                      + security_deposit
                      + cleaning_fee
                      + guests_included
                      + extra_people
                      + minimum_nights
                      + maximum_nights
                      + review_scores_rating
                      + bathrooms
                      + bedrooms
                      + beds
                      + bed_type
                      + availability_30
                      + availability_60
                      + availability_90
                      + availability_365
                      # + neighbourhood_cleansed
                      + number_of_reviews
                      + number_of_reviews_ltm 
                      + review_scores_accuracy 
                      + review_scores_cleanliness
                      + review_scores_checkin
                      #           + review_scores_communication 
                      #            + review_scores_location 
                     + review_scores_value 
                      #            + reviews_per_month 
                      #            + instant_bookable 
                    #  + cancellation_policy 
                      #            + require_guest_profile_picture 
                      #            + require_guest_phone_verification      
                    + calculated_host_listings_count 
                    + calculated_host_listings_count_entire_homes 
                    + calculated_host_listings_count_private_rooms
                    +  name_nchar
                    #            + description_nchar 
                    #            +neighborhood_overview_nchar 
                    + summary_nchar 
                    + space_nchar 
                    #           + notes_nchar 
                    #            + access_nchar 
                    #           + interaction_nchar
                    + amenities_nchar 
                    + first_review_day 
                    + last_review_day 
                    #            + host_since_day 
                     +latitude
                    +longitude
                    + maximum_maximum_nights
                    + minimum_maximum_nights
                    + luxury
                    + transit_modes
                        ,data=data,ntree = 1, na.action=na.exclude)

pred = predict(model2,newdata=scoringData)
rmseForest = sqrt(mean((pred-data$price)^2)); rmseForest
table(is.na(pred))
```

Applying boosting model and for predicting prices and removing non essential variables from the model.

Due to computational limitations reducing trees from 30000 to 1000.

```{r echo=TRUE}
#boosting

set.seed(617)
model3 = gbm(price~ host_total_listings_count
             + host_is_superhost 
             + host_has_profile_pic
             + host_identity_verified
             + is_location_exact
             + property_type
             + neighbourhood_group_cleansed
             + room_type
             + accommodates
             + security_deposit
             + cleaning_fee
             + guests_included
             + extra_people
             + minimum_nights
             + maximum_nights
             + review_scores_rating
             + bathrooms
             + bedrooms
             + beds
             + bed_type
             + availability_30
             + availability_60
             + availability_90
             + availability_365
              + neighbourhood_cleansed
             + number_of_reviews
             + number_of_reviews_ltm 
             + review_scores_accuracy 
             + review_scores_cleanliness
             + review_scores_checkin
             #           + review_scores_communication 
             #            + review_scores_location 
             + review_scores_value 
                         + reviews_per_month 
             #            + instant_bookable 
               + cancellation_policy 
                        + require_guest_profile_picture 
             #            + require_guest_phone_verification      
             + calculated_host_listings_count 
             + calculated_host_listings_count_entire_homes 
             + calculated_host_listings_count_private_rooms
             +  name_nchar
             #            + description_nchar 
             #            +neighborhood_overview_nchar 
             + summary_nchar 
             + space_nchar 
             #           + notes_nchar 
                        + access_nchar 
             #           + interaction_nchar
             + amenities_nchar 
            # + first_review_day 
            # + last_review_day 
             #            + host_since_day 
            +latitude
            +longitude
            + luxury
            + transit_modes
             , data=data, distribution="gaussian", n.trees = 1000,interaction.depth = 8,shrinkage = 0.001)
predBoostTrain = predict(model3,n.trees = 1000)
rmseBoostTrain = sqrt(mean((predBoostTrain-data$price)^2)); rmseBoostTrain

pred = predict(model3,newdata=scoringData, n.trees = 1000)
rmseBoostTest = sqrt(mean((pred-data$price)^2)); rmseBoostTest

table(is.na(pred))
```

Applying ranger model and for predicting prices and removing non essential variables from the model.


```{r eval=FALSE, include=FALSE}
#ranger 

ranger_rf = ranger(formula   = price~host_total_listings_count
                   + host_is_superhost 
                   + host_has_profile_pic
                   + host_identity_verified
                   + is_location_exact
                   + property_type
                   + neighbourhood_group_cleansed
                   + room_type
                   + accommodates
                   + security_deposit
                   + cleaning_fee
                   + guests_included
                   + extra_people
                   + minimum_nights
                   + maximum_nights
                   + review_scores_rating
                   + bathrooms
                   + bedrooms
                   + beds
                   + bed_type
                   + availability_30
                   + availability_60
                   + availability_90
                   + availability_365
                   + neighbourhood_cleansed
                   + number_of_reviews
                   + number_of_reviews_ltm 
                   + review_scores_accuracy 
                   + review_scores_cleanliness
                   + review_scores_checkin
                   #           + review_scores_communication 
                   #            + review_scores_location 
                   + review_scores_value 
                   + reviews_per_month 
                   #            + instant_bookable 
                   + cancellation_policy 
                   + require_guest_profile_picture 
                   #            + require_guest_phone_verification      
                   + calculated_host_listings_count 
                   + calculated_host_listings_count_entire_homes 
                   + calculated_host_listings_count_private_rooms
                   +  name_nchar
                   #            + description_nchar 
                   #            +neighborhood_overview_nchar 
                   + summary_nchar 
                   + space_nchar 
                   #           + notes_nchar 
                   + access_nchar 
                   #           + interaction_nchar
                   + amenities_nchar 
                   # + first_review_day 
                   # + last_review_day 
                               + host_since_daye, 
                   data      = data,num.trees = 500,write.forest = TRUE)
```

Constructing the submission from predictions file

```{r}

submissionFile = data.frame(id = scoringData$id, price = pred)
write.csv(submissionFile, 'boost_submission.csv',row.names = F)

```

